---
title: "Offline Distances"
author: "Cyrus Cravens"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: chaos
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tinytex)   # Helper Functions to Install and Maintain TeX Live, and Compile LaTeX Documents
library(rlang)     # Functions for Base Types and Core R and 'Tidyverse' Features
library(rmarkdown) # Dynamic Documents for R
library(rmdformats)
library(knitr) 
library(tidyverse) # Load core packages:
library(ggplot2)   # data visualization.
library(dplyr)     # data manipulation.
library(tidyr)     # data tidying.
library(readr)     # data import.
library(purrr)     # functional programming.
library(tibble)    # tibbles, a modern re-imagining of data frames.
library(stringr)   # strings.
library(forcats)   # factors.
library(lubridate) # date/times.
library(readr)     # reading .csv, .tsv, and .fwf files.
library(readxl)    # reading .xls, and .xlxs files.
library(feather)   # sharing with Python and other languages.
library(haven)     # SPSS, SAS and Stata files.
library(httr)      # web apis.
library(jsonlite)   # JSON.
library(rvest)     # web scraping.
library(xml2)      # XML.
library(modelr)    # modelling within a pipeline
library(broom)     # turning models into tidy data
library(hms)       # times.
library(magrittr)  # Pipeline operator
library(lobstr)    # Visualizing abstract syntax trees, stack trees, and object sizes
library(pander)    # Exporting/converting complex pandoc documents, EX: df to Pandoc table
library(ggforce)   # More plot functions on top of ggplot2
library(ggpubr)    # Automatically add p-values and significance levels  plots.
library(sf)        # Geo-spatial vector manipulation: points, lines, polygons
library(ff)
library(ldat)
library(rio)
library(jsonlite)
library(reader)
library(qdapRegex)
library(sp)
library(lubridate)
```

```{r}
# Set working directory as needed
#setwd("")
```

# Import & Tidying 
```{r}
load("~/Projects/IPS/src/IPS_offline.RData")
load("~/Projects/IPS/src/IPS_online.RData")
```

## Linear Model To Establish Significance Of Variables

```{r}
# # Setting RSSI as the dependent variable because it is what varies given proximity
# RSSI_lm <- lm(RSSI~posX+posY+orientation+ap_x+ap_y, new_off) # this model excludes the c variable that is distance between receiver and ap
# summary(RSSI_lm) # note: orientation has a p value of 0.432 making it insignificant
```

```{r}
# Setting RSSI as the dependent variable because it is what varies given proximity 
# RSSI_lm2 <- lm(RSSI~posX+posY+orientation+ap_x+ap_y+c, new_off) # this model includes c variable to examine what happens to the p-value for orientation
# summary(RSSI_lm2) # note that the p value for orientation has gotten larger by 20.7% making it non-significant to RSSI values that determine signal strength
```

```{r}
IPS_offline_Data
```
```{r}
IPS_online_Data
```

```{r}
max(IPS_offline_Data$RSSI)-IPS_offline_Data$RSSI[1]
```


### Trimming Offline Data Based On Significance 
```{r}
training <- function(x){
  trimmed <- x[-c(4,8:11)] %>%  # Removing unnecessary offline variables
    mutate(loss = (max(RSSI)-RSSI)) %>% 
    group_by(posX, posY, MAC) %>% 
    mutate(avg_RSSI = mean(RSSI)) %>% 
    mutate(avg_loss = mean(loss)) %>% 
    mutate(sd_RSSI = sd(RSSI)) %>%
    mutate(var_RSSI = var(RSSI))
  rownames(trimmed)<-NULL
  return(trimmed)
}

testing <- function(x){
  no_locs <- x[-c(2:4,7:9,12)] %>% 
    mutate(loss = (max(RSSI)-RSSI)) %>% 
    group_by(MAC, timestamp) %>%
    distinct()
  rownames(no_locs)<-NULL
  return(no_locs)
}

```

```{r}
avg_off <- training(x=IPS_offline_Data)
avg_off 
```

```{r}
avg_on <- testing(x=IPS_offline_Data)
avg_on
```


```{r}
summary(avg_on)
summary(avg_off)
```


```{r}
fingerprints <- function(x){
  reduced <- x %>% select(-c(RSSI, loss)) %>% distinct()
  return(reduced)
}
```

```{r}
off_fp <- fingerprints(avg_off)
on_fp <- avg_on %>% group_by(MAC) %>% distinct()

on_fp
```


```{r}
view(off_fp)
```

```{r}
avg_off_split <- avg_off %>%  group_split(posX, posY)
avg_off_split[1]
```

```{r}
avg_off_split[2]
```


```{r}
avg_off %>% select(avg_RSSI, sd_RSSI) %>% select(-c(posX, posY)) %>%  distinct()
```


```{r}
# off_stats <- reduced_off %>% group_by(posX, posY, MAC) %>% 
#   mutate(avg_RSSI = mean(RSSI)) %>%
#   mutate(error_RSSI = abs(RSSI-avg_RSSI)) %>% 
#   mutate(sd_RSSI = sd(RSSI))
# off_stats
```

```{r}
#
```


```{r}
reduced_off <- new_off %>% distinct()
reduced_off <- as.data.frame(reduced_off)
reduced_off
```

```{r}
reduced_off %>% select(-c(RSSI)) %>% distinct()
```

```{r}
# ap_2.5_0.8 <- trim_acc %>% filter(MAC == "00:14:bf:b1:97:8a")
# ap_1.0_14.0 <- trim_acc %>% filter(MAC == "00:14:bf:b1:97:90")
# ap_7.5_6.3 <- trim_acc %>% filter(MAC == "00:0f:a3:39:e1:c0")
# ap_33.5_9.3 <- trim_acc %>% filter(MAC == "00:14:bf:b1:97:8d")
# ap_33.5_2.8 <- trim_acc %>% filter(MAC == "00:14:bf:b1:97:81")
# ap_12.8_2.8 <- trim_acc %>% filter(MAC == "00:14:bf:3b:c7:c6")
```


```{r eval=FALSE, include=FALSE}
# ap_locs # checking access point locations df
# c_max <- setNames(aggregate(new_off$c, by = list(new_off$MAC), max), c("MAC", "max_dist")) # finding max distance per access point
# c_min <- setNames(aggregate(new_off$c, by = list(new_off$MAC), min), c("MAC", "min_dist")) # finding the minimum distance from access point to offline (x,y) coordinate
# ap_dist <- merge(ap_locs, c_max, by="MAC") # combining c_max df to ap_dist df
# ap_dist <- merge(ap_dist, c_min, by="MAC") # combining c_min df to ap_dist df
# ap_dist
```

## Spliting Offline Data By Receiver Locations

# Visualization Tidying

## Distinct Online Receiver Locations 

```{r}
# finds distinct points to plot for data visualization of online recorded points 
on_rec_locs <- IPS_online_Data %>% 
  select(posX, posY) %>% 
  distinct()
on_rec_locs
#rec_locs[, 2:3] <- sapply(rec_locs[, 2:3], as.geom)
on_rec_locs <- st_as_sf(on_rec_locs, coords = c("posX", "posY"))
plot(on_rec_locs) # checking plot locations
```

## Distinct Offline Receiver Locations 

```{r}
# finds distinct points to plot for data visualization of offline recorded points 
off_rec_locs <- IPS_offline_Data %>% 
  select(posX, posY) %>% 
  distinct()
off_rec_locs
#rec_locs[, 2:3] <- sapply(rec_locs[, 2:3], as.geom)
off_rec_locs <- st_as_sf(off_rec_locs, coords = c("posX", "posY"))
plot(off_rec_locs) # checking plot locations
```

## Access Point Locations
```{r}
# finds distinct points to plot for data visualization of access point locations 
ap_locs <- IPS_offline_Data %>% 
  select(c("MAC", "ap_x", "ap_y")) %>% 
  distinct() %>%  # trimming excess access point locations 
  na.omit()  # removing na values
# ap_locs <- st_as_sf(ap_locs, coords = c("ap_x", "ap_y"))
# ap_locs
# checking results
# plot(ap_locs) # plotting access point locations
```

## Creating Floorplan
```{r}
#MULTILINESTRING
outer <- rbind(c(-0.5,-1.2), c(-0.5,14.2), c(33.8,14.2), c(33.8,-3.4), c(3,-3.4), c(3,-1.2),c(-0.5,-1.2)) #creating exterior outline
low_rms <- rbind(c(3,-1.2), c(3,2.3), c(33.8,2.3))  #creating lower room outline
# Creating lower section separating walls
lw1 <- rbind(c(7.8,2.3), c(7.8,-3.4))
lw2 <- rbind(c(11.3,2.3), c(11.3,-3.4))
lw3 <- rbind(c(16.1,2.3), c(16.1,-3.4))
lw4 <- rbind(c(19.8,2.3), c(19.8,-3.4))
lw5 <- rbind(c(22.1,2.3), c(22.1,-3.4))
lw6 <- rbind(c(24.4,2.3), c(24.4,-3.4))
lw7 <- rbind(c(28,2.3), c(28,-3.4))
lw8 <- rbind(c(30.3,2.3), c(30.3,-3.4))
up_rms <- rbind(c(3,14.2), c(3,9.7), c(33.8,9.7)) #creating upper room outline
# Creating lower section separating walls
uw1 <- rbind(c(9,14.2), c(9,9.7))
uw2 <- rbind(c(11.5,14.2), c(11.5,9.7))
uw3 <- rbind(c(13.8,14.2), c(13.8,9.7))
uw4 <- rbind(c(16.2,14.2), c(16.2,9.7))
uw5 <- rbind(c(19.7,14.2), c(19.7,9.7))
uw6 <- rbind(c(22.1,14.2), c(22.1,9.7))
uw7 <- rbind(c(25.6,14.2), c(25.6,9.7))
uw8 <- rbind(c(28.1,14.2), c(28.1,9.7))
uw9 <- rbind(c(30.5,14.2), c(30.5,9.7))

#creating multilinestring library(sf)
(mls <- st_multilinestring(list(outer,low_rms,lw1,lw2,lw3,lw4,lw5,lw6,lw7,lw8,up_rms,uw1,uw2,uw3,uw4,uw5,uw6,uw7,uw8,uw9)))

plot(mls) # inspecting mls

#MULTIPOLYGON
#center-row LEFT room
p1 <- rbind(c(3,4), c(3,6.7), c(7.9,6.7), c(7.9,4), c(3,4))
#p2 <- rbind(c(3.2,4.2), c(3.2,6.5), c(7.7,6.5), c(7.7,4.2), c(3.2,4.2))
#pol <-st_polygon(list(p1,p2))
#center-row MIDDLE room
p3 <- rbind(c(13.6,4), c(13.6,6.7), c(19.9,6.7), c(19.9,4), c(13.6,4))
#p4 <- rbind(c(13.8,4.2), c(13.8,6.5), c(19.7,6.5), c(19.7,4.2), c(13.8,4.2))
#center-row RIGHT room
p5 <- rbind(c(27,4), c(27,6.7), c(31,6.7), c(31,4), c(27,4))
#p6 <- rbind(c(27.2,4.2), c(27.2,6.5), c(30.8,6.5), c(30.8,4.2), c(27.2,4.2))
#Creating multiple polygons library(sf)
(mpol <- st_multipolygon(list(list(p1), list(p3), list(p5))))

plot(mpol) # inspecting polygon

(sfc=st_sfc(mls, mpol))
```
```{r}
# Creating matrices for receiver and access point locations to pass into st_multipoint function 
# rec_points <- reduced_off %>% select(posX, posY) %>% as.matrix()
# ap_points <- reduced_off %>% select(ap_x, ap_y) %>% as.matrix() 
# 
# # Creating the multipoint sf objects
# rec_mp <- st_multipoint(rec_points, dim = "XY")
# ap_mp <- st_multipoint(ap_points, dim = "XY")
# 
# # Creating multilinestring from multipoints
# # dist_mls <- st_multilinestring(list(rbind(rec_points, ap_points)))
# # dist_mls
# # Create empty example plot
# plot()
# 
# # Draw one line
# segments(x0 = reduced_off$posX, y0 = reduced_off$posY, x1 = reduced_off$ap_x, y1 = reduced_off$ap_y, col = "darkgreen")

```

# Combining Visualizations & Plotting

## Plot Combined Offline Data
```{r}
offline_grid <- ggplot() +
  # inserting floor plan outline
  geom_sf(data = sfc) +
  # inserting ap locations
  geom_point(data = ap_locs, aes(ap_x, ap_y, colour=MAC),

             shape = 15,
             size = 1.5,
             show.legend = NA)+
  # inserting offline receiver locations
  geom_sf(data = off_rec_locs,
             colour = "grey",
             alpha = .8,
             size = 1)+

  xlim(-5, 35)+
  ylim(-5, 15)+
  labs(
    title = "Base Floorplan",
    subtitle = "Grey dots are offline recorded positions whereas blue represents the online",
    # caption = "",
    # tag = "",
    x = "Roughly 35 meters",
    y = "Roughly 18 meters",
    # colour = ""
  )
offline_grid
```

## Plot Combined Online Data
```{r}
online_grid <- ggplot() +
  # inserting floor plan outline
  geom_sf(data = sfc) +
  # inserting ap locations
  geom_point(data = ap_locs, aes(ap_x, ap_y, colour=MAC),

             shape = 15,
             size = 1.5,
             show.legend = NA)+
  
  # inserting online receiver locations
  geom_sf(data = on_rec_locs,
             color = "blue",
             alpha = .3,
             size = 1) +

  xlim(-5, 35)+
  ylim(-5, 15)+
  labs(
    title = "Base Floorplan",
    subtitle = "Grey dots are offline recorded positions whereas blue represents the online",
    # caption = "",
    # tag = "",
    x = "Roughly 35 meters",
    y = "Roughly 18 meters",
    # colour = ""
  )
online_grid
```


## Plot Combined base florplan
```{r}
base_grid <- ggplot() +
  # inserting floor plan outline
  geom_sf(data = sfc) +
  # inserting ap locations
  geom_point(data = ap_locs, aes(ap_x, ap_y, colour=MAC),

             shape = 15,
             size = 1.5,
             show.legend = NA)+
  # inserting offline receiver locations
  geom_sf(data = off_rec_locs,
             colour = "grey",
             alpha = .8,
             size = 1)+
  # inserting online receiver locations
  geom_sf(data = on_rec_locs,
             color = "blue",
             alpha = .3,
             size = 1) +

  xlim(-5, 35)+
  ylim(-5, 15)+
  labs(
    title = "Base Floorplan",
    subtitle = "Grey dots are offline recorded positions whereas blue represents the online",
    # caption = "",
    # tag = "",
    x = "Roughly 35 meters",
    y = "Roughly 18 meters",
    # colour = ""
  )
base_grid
```

### Ploting timeline values

```{r}
# uniq_xy <- 
  new_off %>% select(posX, posY) %>% distinct()
# uniq_xy
```



```{r}
g1 <-  %>% group_split(posX, posY)
g11 <- as.data.frame.list(g1[1])
g11  
  # select(posX, posY, MAC, RSSI, ap_x, ap_y, c) %>% filter(MAC=="00:14:bf:b1:97:90") %>%  distinct()
```